---
title: "Crocheting and plotting: circles vs. spirals"
author: "Katie"
date: "5/23/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Yoga mat bag

I crocheted a yoga mat bag *years* ago. It is cylinder-shaped with a shoulder strap. The base is solid while the body of the cylinder is a net with open spaces. While it works pretty well, I always wished the `radius` was a bit larger so I didn't have to roll the mat so tightly to get it to fit. Also I realized making a net-like tube was not the best idea, because the edges of the mat get caught in the open spaces when I put it in the old bag.

So I just finished my newest attempt at designing and creating a yoga mat bag. I used [Lily Sugar n' Cream yarn]("http://www.yarnspirations.com/yarn/boutiques/lily-sugarn-cream") with a size H (5.0mm) crochet hook for the body of the bag, and a slightly smaller size G (4.5mm) hook for the strap (I wanted the strap to be stitched more closely).

If there's one thing I like as much as crocheting, it's R. And if there's one thing I like better than crocheting or R on their own, it's combining them! I love it when I can get my passions to collide! 

I'm going to use the 'ggplot2' package to help visualize my crochet bag design.

```{r, message = FALSE}
library(ggplot2)
```

I started with six single crochet (sc) stitches in a [magic ring]("") for the inner most part of the circle. Then I immediately start on round 2, working two single crochets into each of the 6 stitches from round one. So round 2 ends up with 12 stitches. I keep going, adding 6 stitches to each round, until I end up with 72 stitches at the end of round 12.

Note that while I said I'm making a circle, I'm technically making a spiral that approximates a circle. I *could* make a pure circle if I wanted to. If I did, I would end each round of the circle by joining the yarn to the first stitch of the round with a slip stitch, then chaining one and 

