---
title: "Yoga mat bag"
author: "Katie"
date: "4/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Yoga mat bag

I crocheted a yoga mat bag *years* ago. It is cylinder-shaped with a shoulder strap. While it works pretty well, I always had two problems with it. 

1. I wish the `radius` was a bit larger so I didn't have to roll the mat so tightly to get it to fit.

2. For the cylinder, I used a stitched that leaves a lot of open space, allowing the edges of the yoga mat to sometimes get caught.

This is my attempt at using *R* to design a bigger and better crocheted yoga mat bag. 

The 'ggplot2' package will help visualize, so let's begin by adding that.

```{r, message = FALSE}
library(ggplot2)
```

The bag is started by making a circle for the bottom of the cylinder. The old bag started with a circle of 12 stitches. To expand on this, I crocheted circles around it, adding 12 stitches for every round until I got to the end of the fifth round. The fifth round had 60 stitches around.


